---
title: "Buncombe Jail Length of Stay - Functions"
author: "DIH"
date: "2023-08-07"
output: html_document
params:
  SHOW_SCRIPT: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, echo=FALSE}
# Ref:
# from console create script of all R chunks
# knitr::purl(input="Report_A_all_dates.Rmd", output="Report_A_all_dates_script.r", documentation=0)
# https://stackoverflow.com/questions/71100718/add-labels-to-pie-chart-ggplot2-after-specifying-factor-orders
# https://dethwench.com/pie-chart-ggplot-style-is-suprisingly-hard/
#
# to get grouping:
# <dataframe> %>% dplyr::group_vars()
```
  
<!-- This file contains only functions. It produces one file, functions.RData, which must be read by other programs. -->
  
```{r}
check_exists <- function(check_){
	# check to see if function name already in use
	if (check_ %in% name_list){
		print(paste("ERROR:",check_,"already exists."))
		knitr::knit_exit()
	} else {
		name_list <- c(name_list, check_)
	}
	#
	return(name_list)
}
```
		
```{r fn_make_pct_stay_plot}
# This shows the percent stay moving across the data. Later dates are biased due to data loss due to future events (that, of course, have not yet happened).  
#
# https://stackoverflow.com/questions/5388832/how-to-get-a-vertical-geom-vline-to-an-x-axis-of-class-date
# https://stackoverflow.com/questions/47901792/annotate-with-ggplot2-when-axis-is-of-class-date
# break in y-axis

# https://cran.r-project.org/web/packages/ggbreak/vignettes/ggbreak.html
# https://github.com/YuLab-SMU/supplemental-ggbreak/blob/main/Rmarkdown/supplementary.Rmd
#
fn_make_pct_stay_plot <- function(df_moving_, title_hdr_, cutoff_=100){
	df_moving_ %>%
		dplyr::filter(
			any(stringr::str_detect(Group, Group_txt[1:4]))
		) %>%
		dplyr::select(
			as_of_date,
			Group,
			pct
		) %>%
		dplyr::mutate(
			Group=factor(Group,levels=c(Group_txt[1:4]))
		) %>%
		ggplot( aes( x = as_of_date, y = pct, color = Group ) ) +
		geom_point() +
		geom_smooth(method = "loess", fill = NA) +
		ylim(0,cutoff_)+
		labs( 
			x = "As-Of Date", 
			y = "Percent of Stay", 
			title = paste(title_hdr_,"Percent Length of Stay Buncombe County Jail Inmates",FILE_DATE,"Data"),
			subtitle = ifelse(cutoff_==100,"",paste0("Vertical Axis Cutoff at ",cutoff_,"%")),
			color = NULL
		) +
		scale_color_discrete(
			labels = c(Group_txt[1:4])
		) +
		theme( 
			axis.text.x = element_text(angle=60, hjust=1), 
			plot.title = element_text(hjust = 0.5),
			plot.subtitle = element_text(hjust = 0.5),
			legend.position = "top"
		) +
		scale_x_date(date_breaks = "months", date_labels = "%d-%m-%Y") 
		#
		# default return
		#
}
```
```{r, echo=FALSE}
name_list <- "fn_make_pct_stay_plot"
```
```{r fn_make_N_stay_plot}
fn_make_N_stay_plot <- function(df_moving, title_hdr_){
	df_moving %>%
		dplyr::filter(
			any(stringr::str_detect(Group, Group_txt[1:4]))
		) %>%
		dplyr::select(
			as_of_date,
			Group,
			N
		) %>%
		dplyr::mutate(
			Group = factor(Group, levels=c(Group_txt[4:1]))
		) %>%
		ggplot( aes( x = as_of_date, y = N ) ) +
		geom_point(size=0.5) +
		facet_wrap(
			vars(Group), 
			ncol=1, 
			strip.position="bottom"
		) +
		labs( 
			x = "As-Of Date", 
			title = paste(title_hdr_,"Length of Stay Buncombe County Jail Inmates",FILE_DATE,"Data")
		) +
		theme( 
			axis.text.x = element_text(angle=60, hjust=1), 
			plot.title = element_text(hjust = 0.5),
			plot.subtitle = element_text(hjust = 0.5),
			legend.position = "top"
		) +
		scale_x_date(date_breaks = "months", date_labels = "%d-%m-%Y") 
		#
		# default return
		#
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_make_N_stay_plot")
```
```{r fn_make_pct_stay_plot_one_up}
fn_make_pct_stay_plot_one_up <- function(df_moving_, select_group_, cutoff_=100){
	# select_group_ is the index of the item in Group_txt
	df_moving_ %>%
		dplyr::filter(
			Group == Group_txt[select_group_]
		) %>%
		dplyr::select(
			as_of_date,
			Group,
			pct
		) %>%
		ggplot( aes( x = as_of_date, y = pct) ) +
		geom_point() +
		geom_smooth(method = "loess", fill = NA) +
		ylim(0,cutoff_) +
		labs( 
			x = "As-Of Date", 
			y = "Percent of Stay", 
			title = paste(Group_txt[select_group_],"Percent Length of Stay",FILE_DATE,"Data"),
			subtitle = ifelse(cutoff_==100,"",paste0("Vertical Axis Cutoff at ",cutoff_,"%")),
			color = NULL
		) +
		theme( 
			axis.text.x = element_text(angle=60, hjust=1), 
			plot.title = element_text(hjust = 0.5),
			plot.subtitle = element_text(hjust = 0.5),
			legend.position = "none"
		) +
		scale_x_date(date_breaks = "months", date_labels = "%d-%m-%Y") 
		#
		# default return
		#
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_make_pct_stay_plot_one_up")
```
```{r fn_make_N_stay_plot_one_up}
fn_make_N_stay_plot_one_up <- function(df_moving_, cutoff_, select_group_, which_offense_){
	# select_group_ is the index of the item in Group_txt
	df_moving_ %>%
		dplyr::filter(
			Group == Group_txt[select_group_]
		) %>%
		dplyr::select(
			as_of_date,
			Group,
			N
		) %>%
		ggplot( aes( x = as_of_date, y = N) ) +
		geom_point() +
		geom_smooth(method = "loess", fill = NA) +
		ylim(0,cutoff_) +
		labs( 
			x = "As-Of Date", 
			y = "Number of Inmates", 
			title = paste(which_offense_,Group_txt[select_group_],FILE_DATE,"Data"),
			color = NULL
		) +
		theme( 
			axis.text.x = element_text(angle=60, hjust=1), 
			plot.title = element_text(hjust = 0.5),
			plot.subtitle = element_text(hjust = 0.5),
			legend.position = "none"
		) +
		scale_x_date(date_breaks = "months", date_labels = "%d-%m-%Y") 
		#
		# default return
		#
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_make_N_stay_plot_one_up")
```
```{r fn_inmates_overall}
# this finds the df_daily_inmates record with the earliest import date
fn_inmates_overall <- function(df_daily_inmates_){
	df_inmates_overall_ <- 
		df_daily_inmates_ %>% 
			dplyr::select(
				import_date,
				name,
				arrested
			) %>% 
			dplyr::group_by(
				name,
				arrested
			) %>% 
			dplyr::summarise(
				max_import_date = max(import_date),
				min_import_date = min(import_date)
			) %>% 
			dplyr::ungroup() %>% 
			dplyr::mutate(
				stay = max_import_date - min_import_date + 1
			)
#
	return(df_inmates_overall_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_inmates_overall")
```
```{r fn_inmates_overall_supp}
# this extends to include useful ancillary items
fn_inmates_overall_supp <- function(df_inmates_overall_,df_daily_inmates_){
	df_inmates_overall_supp_ <- 
		dplyr:::left_join(
			df_inmates_overall_,
			df_daily_inmates_,
			by=c(
				"min_import_date"="import_date",
				"name",
				"arrested"
			)
		) %>%
		dplyr::rename(
			import_date = min_import_date
		) %>%
		dplyr::select(
			defendant_id,
			import_date,
			name,
			arrested,
			max_import_date,
			stay,
			race,
			gender,
			age,
			total_bond
		)
	#
	return(df_inmates_overall_supp_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_inmates_overall_supp")
```
```{r fn_inmates_overall_arr}
fn_inmates_overall_arr <- function(df_daily_inmates_){
	# this finds the df_daily_inmates record with the earliest import date
	df_inmates_overall_arr_ <- 
		df_daily_inmates_ %>% 
			dplyr::select(
				import_date,
				name,
				arrested
			) %>% 
			dplyr::group_by(
				name,
				arrested
			) %>% 
			dplyr::summarise(
				max_import_date = max(import_date),
				min_import_date = min(import_date)
			) %>% 
			dplyr::ungroup() %>% 
			dplyr::mutate(
				min_import_date_hold = min_import_date,
				min_import_date = as.Date(ifelse(arrested < min_import_date, arrested, min_import_date),"1970-01-01"),
				stay = max_import_date - min_import_date + 1
			)
	#
	return(df_inmates_overall_arr_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_inmates_overall_arr")
```
```{r fn_inmates_overall_arr_supp}
fn_inmates_overall_arr_supp <- function(df_inmates_overall_arr_,df_daily_inmates_){
	# this extends to include useful ancillary items
	df_inmates_overall_arr_supp_ <- 
		dplyr:::left_join(
			df_inmates_overall_arr_,
			df_daily_inmates_,
			by=c(
				"min_import_date_hold"="import_date",
				"name",
				"arrested"
			)
		) %>%
		dplyr::rename(
			import_date = min_import_date
		) %>%
		dplyr::select(
			defendant_id,
			import_date,
			name,
			arrested,
			max_import_date,
			stay,
			race,
			gender,
			age,
			total_bond
		)
	#
	return(df_inmates_overall_arr_supp_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_inmates_overall_arr_supp")
```
```{r fn_n_cur_count_by_date, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_n_cur_count_by_date <- function(df_daily_inmates_){
	df_n_cur_count_by_date_ <- 
		df_daily_inmates_ %>% 
			dplyr::group_by(
				import_date
			) %>%
		dplyr::tally() %>%
		dplyr::rename(
			N = n
		) %>% 
		dplyr::inner_join(
			df_daily_inmates_ %>%
				reshape2::dcast(
					import_date ~ gender, fun.aggregate=length
				),
			by = "import_date"
		) %>%
		dplyr::inner_join(
			df_daily_inmates_ %>%
				dplyr::filter(
					race == "B" | race == "W"
				) %>%
				reshape2::dcast(
					import_date ~ race, fun.aggregate=length
				),
			by = "import_date"
		) %>%
		dplyr::inner_join(
			df_daily_inmates_ %>%
				dplyr::filter(
					race == "B" | race == "W"
				) %>%
				reshape2::dcast(
					import_date ~ race + gender, fun.aggregate=length
				),
			by = "import_date"
		)
	#
	return(df_n_cur_count_by_date_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_n_cur_count_by_date")
```
```{r fn_n_cur_count_by_date_matrix, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_n_cur_count_by_date_matrix <- function(df_n_cur_count_by_date_){
	df_n_cur_count_by_date_ %<>%
		dplyr::mutate(
			Fpct = 100*round(F/N, digits=3),
			Mpct = 100*round(M/N, digits=3),
			Bpct = 100*round(B/N, digits=3),
			Wpct = 100*round(W/N, digits=3),
			B_Fpct = 100*round(B_F/N, digits=3),
			B_Mpct = 100*round(B_M/N, digits=3),
			W_Fpct = 100*round(W_F/N, digits=3),
			W_Mpct = 100*round(W_M/N, digits=3),
			Flogit = round(qwraps2::logit(Fpct/100), digit=3),
			Mlogit = round(qwraps2::logit(Mpct/100), digit=3),
			Blogit = round(qwraps2::logit(Bpct/100), digit=3),
			Wlogit = round(qwraps2::logit(Wpct/100), digit=3),
			B_Flogit = round(qwraps2::logit(B_Fpct/100), digit=3),
			B_Mlogit = round(qwraps2::logit(B_Mpct/100), digit=3),
			W_Flogit = round(qwraps2::logit(W_Fpct/100), digit=3),
			W_Mlogit = round(qwraps2::logit(W_Mpct/100), digit=3)
		)
	#
	return(df_n_cur_count_by_date_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_n_cur_count_by_date_matrix")
```
```{r fn_mult_names}
fn_mult_names <- function(df_inmates_overall_){
	# multiple instances for these names:
	df_mult_names_ <- 
		df_inmates_overall_ %>% 
			dplyr::ungroup() %>% 
			dplyr::select(
				name
			) %>% 
			dplyr::group_by(
				name
			) %>% 
			dplyr::count() %>% 
			dplyr::filter(
				n>1
			) %>%
			dplyr::ungroup()
	#
	return(df_mult_names_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_mult_names")
```
```{r fn_mult_names_dates}
fn_mult_names_dates <- function(df_mult_names_,df_inmates_overall_arr_){
	# incorporate arrested and max_import_date
	df_mult_names_dates_ <- 
		dplyr::inner_join(
			df_mult_names_ %>% 
				dplyr::select(
					name
				),
			df_inmates_overall_arr_ %>% 
				dplyr::select(
					name,
					arrested,
					max_import_date,
					stay
				),
			by="name"
		)
	#
	return(df_mult_names_dates_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_mult_names_dates")
```
```{r fn_mult_names_strung}
fn_mult_names_strung <- function(df_mult_names_dates_){
	df_mult_names_strung_ <- data.frame(matrix(ncol = 4, nrow = nrow(df_mult_names_dates_)))
	# column "type" is a dummy that is thrown away
	colnames(df_mult_names_strung_) <- c("name","arrested","max_import_date","type")
	#
	out_ <- 1
	for (i in 1:nrow(df_mult_names_dates_)){
		if (i == 1){
			# get started
			prev_name <- df_mult_names_dates_[i, "name"]
			prev_arrested <- df_mult_names_dates_[i, "arrested"]
			prev_mid <- df_mult_names_dates_[i, "max_import_date"]
			# 
			# write first part of first record
			df_mult_names_strung_[out_,"name"] <- prev_name
			df_mult_names_strung_[out_,"arrested"] <- prev_arrested
		} else {
			this_name <- df_mult_names_dates_[i, "name"]
			this_arrested <- df_mult_names_dates_[i, "arrested"]
			this_mid <- df_mult_names_dates_[i, "max_import_date"]
			# 
			# compare to previous
			# if not a continuation, write completed record
			# if continuation, reset pointers
			if (this_name == prev_name & prev_mid == this_arrested){
				# continuation
				prev_arrested <- this_arrested
				prev_mid <- this_mid
				df_mult_names_strung_[out_,"type"] <- "C"
			} else {
				# finish writing out record
				df_mult_names_strung_[out_,"max_import_date"] <- prev_mid
				#
				# advance to next out record
				out_ <- out_ + 1
				#
				# reset pointers
				prev_name <- this_name
				prev_arrested <- this_arrested
				prev_mid <- this_mid
				#
				# write first part of first record
				df_mult_names_strung_[out_,"name"] <- prev_name
				df_mult_names_strung_[out_,"arrested"] <- prev_arrested
			}
		}	
	}
	rm(this_name,this_arrested,this_mid)
	#
	# drop the rows where "type" is NA by using na.omit
	df_mult_names_strung_ %<>% 
		na.omit() %>% 
		dplyr::select(
			-type
		) %>%
		dplyr::mutate(
			arrested = as.Date(arrested,origin="1970-01-01"),
			max_import_date = as.Date(max_import_date,origin="1970-01-01"),
			stay = max_import_date - arrested + 1
		)
	#
	return(df_mult_names_strung_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_mult_names_strung")
```
```{r fn_daily_inmates_prep_0}
fn_daily_inmates_prep_0 <- function(df_daily_inmates_){
	df_daily_inmates_strung_0_ <-
		df_daily_inmates_ %>%
			dplyr::select(
				import_date,
				name,
				arrested
			) %>%
			dplyr::mutate(
				id = 2
			)
	#
	return(df_daily_inmates_strung_0_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_daily_inmates_prep_0")
```
```{r fn_daily_inmates_prep_add}
fn_daily_inmates_prep_add <- function(df_mult_names_strung_,N_mult_names_strung_stay_){
	#
	# use df_mult_names_strung to create rows, one for each day
	# pick dates from CURRENT_DATES to account for the missing data
	#
	df_daily_inmates_strung_add_ <- data.frame(matrix(ncol = 4, nrow = N_mult_names_strung_stay_))
	# column "type" is a dummy that is thrown away
	colnames(df_daily_inmates_strung_add_) <- c("import_date","name","arrested","id")
	#
	i_ <- 1
	for (j_ in 1:nrow(df_mult_names_strung_)){
		this_name <- df_mult_names_strung_[j_,"name"]
		this_arrested <- df_mult_names_strung_[j_,"arrested"]
		CURRENT_DATES_start <- which(CURRENT_DATES == this_arrested)
		this_mid <- df_mult_names_strung_[j_,"max_import_date"]
		N_days_ <- as.integer(this_mid - this_arrested)
		for (k_ in 0:N_days_){
			df_daily_inmates_strung_add_[i_,"import_date"] <- this_arrested + k_
			df_daily_inmates_strung_add_[i_,"name"] <- this_name
			df_daily_inmates_strung_add_[i_,"arrested"] <- this_arrested
			df_daily_inmates_strung_add_[i_,"id"] <- 1
			i_ <- i_+1
		}
	}
	rm(this_name,this_arrested,this_mid,N_days_)
	rm(i_,j_,k_)
	#
	df_daily_inmates_strung_add_ %<>% 
		dplyr::mutate(
			import_date = as.Date(import_date,origin = "1970-01-01"),
			arrested = as.Date(arrested,origin = "1970-01-01")
		)
	#
	return(df_daily_inmates_strung_add_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_daily_inmates_prep_add")
```
```{r fn_inmates_overall_strung}
fn_inmates_overall_strung <- function(df_daily_inmates_strung_){
	# this finds the df_daily_inmates record with the earliest import date
	df_inmates_overall_strung_ <- 
		df_daily_inmates_strung_ %>% 
			dplyr::select(
				import_date,
				name,
				arrested
			) %>% 
			dplyr::group_by(
				name,
				arrested
			) %>% 
			dplyr::summarise(
				max_import_date = max(import_date),
				min_import_date = min(import_date)
			) %>% 
			dplyr::ungroup() %>% 
			dplyr::mutate(
				stay = max_import_date - min_import_date + 1
			)
	#
	return(df_inmates_overall_strung_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_inmates_overall_strung")
```
```{r fn_daily_inmates_g_count_melt}
fn_daily_inmates_g_count_melt <- function(df_daily_inmates_){
	df_daily_inmates_g_count_melt_ <-
		df_daily_inmates_ %>%
			dplyr::filter(
				holding_facility == "CENTRAL" | holding_facility == "MAIN JAIL"
			) %>% 
			dplyr::group_by(
				holding_facility
			) %>% 
			reshape2::dcast(import_date ~ holding_facility) %>%
			dplyr::mutate(
				TOTAL = CENTRAL + `MAIN JAIL`
			) %>%
			reshape2::melt(
				id.vars = "import_date",
				variable.name = "holding_facility",
				value.name = "N"
			)
	#
	return(df_daily_inmates_g_count_melt_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_daily_inmates_g_count_melt")
```
```{r fn_make_daily_inmates_plot}
fn_make_daily_inmates_plot <- function(df_daily_inmates_g_count_melt_){
	# holding_facility counts:
	df_daily_inmates_g_count_melt_ %>%
		ggplot( aes( x = import_date, y = N, color = holding_facility ) ) +
		geom_point() +
		ylim(0,500) +
		labs( 
			x = "Import Date", 
			y = "Inmates", 
			title = paste("A1. Buncombe County Jail Inmates",FILE_DATE,"Data"),
			subtitle = "CENTRAL and MAIN JAIL",
			color = NULL
		) +
		theme( 
			axis.text.x = element_text(angle=60, hjust=1), 
			plot.title = element_text(hjust = 0.5),
			plot.subtitle = element_text(hjust = 0.5),
			legend.position = "top"
		)+
		scale_x_date(date_breaks = "months", date_labels = "%d-%m-%Y")
	#
	# default return
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_make_daily_inmates_plot")
```
```{r fn_prep_earliest}
fn_prep_earliest <- function(df_daily_inmates_,df_inmates_overall_){
	# MUST START AT CURRENT_DATES[1] + 91 TO AVOID DISTORTIONS
	df_prep_earliest_ <-
		dplyr::inner_join(
			df_daily_inmates_ %>% 
			dplyr::ungroup() %>%
			dplyr::select(
				import_date,
				name,
				arrested
			),
			df_inmates_overall_ %>%
				dplyr::select(
					name,
					arrested,
					min_import_date
				),
			by = c("name","arrested")
		) %>%
		dplyr::select(
			import_date,
			min_import_date
		) %>%
		dplyr::rename(
			this_date = min_import_date
		) %>%
		dplyr::mutate(
			eff_stay = import_date - this_date + 1
		)
	#
	return(df_prep_earliest_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_prep_earliest")
```
```{r fn_make_mean_stay_compare_plot}
fn_make_mean_stay_compare_plot <- function(
	df_prep_earliest_ = df_prep_earliest, 
	df_prep_arrested_ = df_prep_arrested, 
	df_prep_strung_arrested_ = df_prep_strung_arrested
){
	#
	# baked in comparison dataframes
	# df_prep_earliest, df_prep_arrested, df_prep_strung_arrested
	#
	df_<- rbind(
		df_prep_earliest_ %>%
			dplyr::mutate(
				DF = "Earliest"
			),
		df_prep_arrested_ %>%
			dplyr::mutate(
				DF = "Arrested"
			),	
		df_prep_strung_arrested_ %>%
			dplyr::mutate(
				DF = "Strung"
			)	
	) %>%
	dplyr::group_by(
		DF,
		import_date
	) %>%
	dplyr::filter(
		import_date > "2022-01-02"
	) %>%
	dplyr::summarize(
		mean = as.numeric(mean(eff_stay))
	)
	#
	df_$DF <- factor( df_$DF, levels = c( "Strung", "Arrested", "Earliest" ))
	
	plot_ <- df_ %>%
	ggplot( aes( x = import_date, y = mean) ) +
	geom_point( aes( color = DF ) ) +
	scale_color_manual( values = c("#6600FF", "#FF0033", "#669900") ) +
	labs( 
		title = "Mean Stay for Strung, Arrested, and Earliest Date Methods",
		subtitle = paste(FILE_DATE, "Data"),
		color = NULL
	) +
	theme(
		plot.title = element_text(hjust = 0.5),
		plot.subtitle = element_text(hjust = 0.5),
		legend.position = "top"
	)
	#
	return(plot_)
}
```
```{r, echo=FALSE}
name_list <- check_exists("fn_make_mean_stay_compare_plot")
```

```{r fn_compute_stay_by_day, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_compute_stay_by_day <- function(df_){
	# using df_inmate_stays_summ  
	# helpers
	df_1_ <- data.frame(
		matrix(
			ncol = length(CURRENT_DATES), 
			nrow = nrow(df_)
		)
	)
	#
	names(df_1_) <- as.character(as.numeric(CURRENT_DATES[1:length(CURRENT_DATES)]))
	#
	df_2_ <-
		df_ %>%
			dplyr::select(
				defendant_id,
				stay,
				start_date,
				end_date
			) %>%
			dplyr::mutate(
				end_date = as.Date( ifelse( is.na(end_date), CURRENT_DATES[length(CURRENT_DATES)], end_date ), origin = "1970-01-01"),
				start_date = as.numeric(start_date),
				end_date = as.numeric(end_date)
			) 
	#
	df_target_ <- cbind(
		df_2_,
		df_1_
	)
	# change df_2_
	df_2_$S <- NA
	#
	rm( df_1_ )
	#
	# do the work
	#
	col_num_ <- 5
	for (cd_ in CURRENT_DATES[1:length(CURRENT_DATES)]){
		cd_date_ <- as.numeric(cd_)
		#
		df_2_%<>%
			dplyr::mutate(
				S =
				ifelse( end_date < cd_date_ | start_date > cd_date_, NA, 
						 cd_date_ - start_date + 1
					)
			)
		#
		df_target_[,col_num_] <- df_2_$S
		col_num_ <- col_num_ + 1
	}
	#
	return(df_target_)
}
```
```{r}
name_list <- check_exists("fn_compute_stay_by_day")
```
```{r fn_stay_by_day_melt, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_stay_by_day_melt <- function(df_){
	# using df_stay_by_day
	df_freq_ <- 
		df_ %>% 
			dplyr::select(
				-stay,
				-start_date,
				-end_date
			) %>% 
		reshape2::melt(
			id.vars="defendant_id"
		) %>% 
		na.omit()
	#
	df_freq_$variable <- as.character.factor(df_freq_$variable)
	#
	df_freq_ %<>%
		dplyr::mutate(
			as_of_date = as.Date(as.numeric(variable), origin="1970-01-01")
		) %>%
		dplyr::select(
			defendant_id,
			value,
			as_of_date
		) %>%
		dplyr::rename(
			stay = value
		)
	#
	return(df_freq_)
}
```
```{r}
name_list <- check_exists( "fn_stay_by_day_melt")
```
2023-08-03:  
```{r fn_stay_by_day_melt_bins, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_stay_by_day_melt_bins <- function(df_in_){
	# using df_stay_by_day_melt
	df_ <- 
		df_in_ %>%
			dplyr::select(
				stay,
				as_of_date
			) %>%
			dplyr::mutate(
				Group = ifelse( stay <= 7, "bin1",
					(ifelse( stay > 7 & stay <= 30, "bin2",
						(ifelse( stay > 30 & stay <= 90, "bin3",
							"bin4" 
				)))))
			) %>%
			reshape2::dcast(
				as_of_date + Group ~ ., 
				length
			) %>%
			dplyr::rename(
				N = '.'
			) %>%
			reshape2::dcast(
				as_of_date ~ Group, 
				value.var="N"
			) 
	#
	df_ %<>% 
		replace( is.na(.), 0 )
	#
	df_ %<>%
		dplyr::mutate(
			N = rowSums(across(where(is.numeric))),
			pct1 = round(100*bin1/N, digits=2),
			pct2 = round(100*bin2/N, digits=2),
			pct3 = round(100*bin3/N, digits=2),
			pct4 = round(100*bin4/N, digits=2)
		)		
}
```
```{r}
name_list <- check_exists( "fn_stay_by_day_melt_bins")
```
2023-08-03:  
```{r fn_pct_bins_stay_by_day_melt, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_pct_bins_stay_by_day_melt <- function(df_in_){
	# using df_stay_by_day_melt_bins
	df_ <-
		df_in_ %>%
			dplyr::select(
				as_of_date,
				pct1,
				pct2,
				pct3,
				pct4
			) %>%
			reshape2::melt(
				id.vars = "as_of_date"
			) %>%
			dplyr::rename(
				Group = variable,
				pct = value
			) %>%
			dplyr::mutate(
				Group = ifelse( Group=="pct1", Group_txt[1],
					(ifelse( Group=="pct2", Group_txt[2],
						(ifelse( Group=="pct3", Group_txt[3],
							Group_txt[4]
				)))))
			)
	#
	return(df_)
}
```{r}
name_list <- check_exists( "fn_pct_bins_stay_by_day_melt")
```
2023-08-03:  
```{r fn_N_bins_stay_by_day_melt, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_N_bins_stay_by_day_melt <- function(df_in_){
	# using df_stay_by_day_melt_bins
	df_ <-
		df_in_ %>%
			dplyr::select(
				as_of_date,
				bin1,
				bin2,
				bin3,
				bin4
			) %>%
			reshape2::melt(
				id.vars = "as_of_date"
			) %>%
			dplyr::rename(
				Group = variable,
				N = value
			) %>%
			dplyr::mutate(
				Group = ifelse( Group=="bin1", Group_txt[1],
					(ifelse( Group=="bin2", Group_txt[2],
						(ifelse( Group=="bin3", Group_txt[3],
							Group_txt[4]
				)))))
			)
	#
	return(df_)
}
```{r}
name_list <- check_exists( "fn_N_bins_stay_by_day_melt")
```
2023-08-04:  
```{r fn_stay_by_day_ml_MF, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_stay_by_day_ml_MF <- function(df_in_,levels_){	
	# using df_inmate_stays_summ
	df_ <- fn_compute_stay_by_day(
		df_in_ %>% 
		dplyr::filter(
			max_level %in% levels_
		)
	)
	#
	return(df_)
}
```{r}
name_list <- check_exists( "fn_stay_by_day_ml_MF")
```
```{r fn_stay_by_day_weighted_freq, message=FALSE, warning=FALSE, echo=params$SHOW_SCRIPT}
fn_stay_by_day_weighted_freq <- function(df_){
	# using df_stay_by_day
	df_freq_ <- 
		df_ %>% 
			dplyr::select(
				-defendant_id,
				-stay,
				-start_date,
				-end_date
			) %>% 
		reshape2::melt() %>% 
		na.omit() %>% 
		reshape2::dcast(
			variable + value ~ ., 
			length
		) 
	#
	df_freq_$variable <- as.character.factor(df_freq_$variable)
	#
	df_freq_ %<>%
		dplyr::mutate(
			as_of_date = as.Date(as.numeric(variable), origin="1970-01-01")
		) %>%
		dplyr::rename(
			stay = value,
			N = '.'
		) %>% 
		dplyr::select(
			-variable
		)
	#
	return(df_freq_)
}
```
```{r}
name_list <- check_exists("fn_stay_by_day_weighted_freq")
```

```{r fn_stay_by_day_tables}
fn_stay_by_day_tables <- function(df_in_){
	# using df_stay_by_day
	df_ <- apply(
		(df_in_ %>% 
			dplyr::select(
				-defendant_id,
				-stay,
				-start_date,
				-end_date
			)
		),
		2,
		as.data.frame(table)
	)
	#
	return(df_)
}
```
```{r}
name_list <- check_exists("fn_stay_by_day_tables")
```
```
```{r save_names}
# produce the RData file that contains all these functions
save(
	list=name_list, 
	file=paste0(RDataPath,"functions.RData")
)
```
